\chapter*{Preface}

This text is an expansion upon notes taken during TAM7960 entitled ``Legged locomotion of robots and animals
(Mechanics of terrestrial locomotion)'' at Cornell University, a course about mechanical models and empirical studies of legged terrestrial locomotion. The goal of the course is to shed light on the coordination, speed, energetics, and stability of locomotion in legged animals, especially humans. The notes were taken during the Spring 2010 offering of the course. This bulk of this text was written during the Fall 2010-Spring 2011 academic year.

This course and the material presented in this book present a variety of ways to model locomotion and analyze the stability and energy effectiveness of both actively and passively controlled versions of the various models. Miscellaneous topics arise throughout; some properties of electric motors, biological muscles, and central pattern generators will also be discussed in brief.

\chapter*{Work flow [temporary section]}

This section is a temporary section  to be used by the people working on the text. A more thorough documentation, include running meeting notes, etc. and a to-do list, are maintained as text files along with the .TEX source files. This provides perhaps a summary overview of such information.

\section*{Alan}

Working on sections:

\begin{itemize}
\item Introduction (needs some freshening up)
\item Motors and muscles ``complete"

\item Passive: stability-related sections
\begin{itemize}
\item Rimless wheel ``complete" (perhaps add a little stability information)
\item SLIP stability ``complete"
\item Simplest walker, ``complete" (perhaps add a little stability information)
\end{itemize}

\item Needed: Figure captions at the end of optimization ``complete"

\item Controlling ``complete" (CPG Section dropped for the first draft, still exists in the comments)
\item Energetics: optimal control ``complete''

\item Using Snopt (Appendix A) Could use some serious revision. I've somewhat forgotten how to use it. I could probably work through it again, unless someone with a good understanding of it could whip it up in a jiff... it would be pretty cool to have a nice detailed tutorial (with screenshots) in here on SNOPT or FMINCON (I think?) or other optimization packages, as they are pretty useful to this field (and in general). 

\end{itemize}

\section*{Chris}

It means that the writing is complete, it's been reviewed once, but is not complete simply because I'm sure it will need revision.

\begin{itemize}
\item Bits of introduction ``complete''
\item Modeling: ``complete'', with about 6-8 comments throughout, except for figure captions
\item Passive: dynamics-related sections

\begin{itemize}
\item rimless wheel: ``complete''
\item simplest walker: ``complete''
\end{itemize}

\item Energetics: requires elaboration/text on Figure 6.2 ParticleExplosion, Ruina's Rant, and about 4 comments/questions throughout ``mostly complete''
\item Optimization: energy optimization expeirments: ``complete''
\item Similarity: want to add more material from McMahon's book in relation to muscles, otherwise ``complete''.
\end{itemize}

\section*{Professor Ruina}

If Professor Ruina is interested, perhaps he could help with the Further Reading section, more immediately. It is likely that he could develop this section much quicker than either Alan or Chris.